---
title: "Compiler"
author: "Patrisha C. Miller"
date: "2024-07-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Compiler

Uses the input of a folder filled with other monthly data folders and outputs into one folder, combining all of the loggers with the same name per month/download into one file each.

```{r, echo=FALSE,include=FALSE}

#Load in packages
library(readxl);library(writexl);library(dplyr);library(fs);library(lubridate)

```

## Main Funtion

The following are my own personal input and output folders that link to my desktop. Hopefully I can figure out how to get it to link to git or some other online resource.

```{r}

input_folder <- "C:\\Users\\patri\\OneDrive - Chatham University\\2024 Summer\\Monthly Data FIXED DATES"    
output_folder <- "C:\\Users\\patri\\OneDrive - Chatham University\\2024 Summer\\Compiled2"

```

```{r}

consolidate_logger_data <- function(input_folder, output_folder) {
  
  # List all subfolders (monthly folders) within the input folder
  monthly_folders <- dir_ls(input_folder, type = "directory")
  
  # Initialize a list to store data for each logger
  logger_data <- list()
  
  # Define a pattern to match the date in the filename
  date_pattern <- "\\d{4}-\\d{2}-\\d{2}"
  
  # Loop through each monthly folder
  for (monthly_folder in monthly_folders) {
    # List all Excel files in the monthly folder
    excel_files <- dir_ls(monthly_folder, glob = "*.xlsx")
    
    # Process each Excel file
    for (excel_file in excel_files) {
      # Extract the logger name (part before the date)
      logger_name <- sub(paste0(" ", date_pattern, ".*"), "", basename(excel_file))
      
      # Read the Excel file
      data <- read_excel(excel_file)
      
      # Remove the first column as it is arbitrary
      data <- data[-1]
      
      # Rename the first and second columns to "DateTime" and "Temperature" respectively
      colnames(data)[1] <- "DateTime"
      colnames(data)[2] <- "Temperature"
      
      # Convert the Excel numeric date-time values to POSIXct
      data$DateTime <- as.POSIXct(data$DateTime, origin = "1899-12-30", tz = "UTC")
      
      # Initialize the list for this logger if it doesn't exist
      if (is.null(logger_data[[logger_name]])) {
        logger_data[[logger_name]] <- list()
      }
      
      # Append data to the corresponding logger's list
      logger_data[[logger_name]] <- append(logger_data[[logger_name]], list(data))
    }
  }
  
  # Create the output folder if it doesn't exist
  if (!dir_exists(output_folder)) {
    dir_create(output_folder)
  }
  
  # Loop through the list of loggers
  for (logger_name in names(logger_data)) {
    # Combine data for the logger
    combined_data <- bind_rows(logger_data[[logger_name]])
    
    # Remove duplicate date-time entries, based on the DateTime column
    combined_data <- combined_data %>%
      distinct(across(all_of("DateTime")), .keep_all = TRUE)
    
    # Sort the data by the DateTime column
    combined_data <- combined_data %>%
      arrange(DateTime)
    
    # Write the consolidated data to an Excel file
    write_xlsx(combined_data, path = file.path(output_folder, paste0(logger_name, ".xlsx")))
  }
}

```



## Using the Function

```{r}

consolidate_logger_data(input_folder, output_folder)

```